# ETAS.inlabru for making synthetic temporal ETAS catalogues

# Installing some extra packages to make sure the main packages work 

```{r}
install.packages("lemon")
install.packages("tidyquant")
install.packages("foreach")
install.packages("GGally")
install.packages("INLA",repos=c(getOption("repos"),INLA="https://inla.r-inla-download.org/R/stable"), dep=TRUE)

```

# The main packages to run the code 

```{r}

library(ETAS.inlabru)
library(ggplot2)
library(dplyr)
```

# Creating the catalogue

- Step 1: Define ETAS parameters
- Step 2: Define model domain
- Step 3: Generate ETAS sample
- Step 4: Combine different lists of different generation earthquakes 
- Step 4: Plot the results

# Define ETAS parameters 

```{r}
mu <- 1000./365
K <- 0.089
alpha <- 2.29
c <- 0.011
p <- 1.08


theta_etas <- data.frame(mu=mu, K=K, alpha=alpha, c=c, p=p)

```


# Define model domain 


```{r}

M0 = 2
modelledDuration = 10000  # [days]

```

# Generate ETAS Sythetic


```{r}

samp.etas.list <- generate.temporal.ETAS.synthetic(theta = theta_etas, beta.p = log(10), M0 = M0, T1 = 0, T2 = modelledDuration)

```

# Combine lists of differnet generation earthqaukes to crete one big catalogue 

```{r}
combined.M7.ETAS.cat <- bind_rows(samp.etas.list)

combined.M7.ETAS.cat <- combined.M7.ETAS.cat[order(combined.M7.ETAS.cat$ts),]

combined.M7.ETAS.cat$ID = seq(1,length(combined.M7.ETAS.cat$ts))

```
# Create The interevent time catalogue 

```{r}
N=length(combined.M7.ETAS.cat$ts)
iet =combined.M7.ETAS.cat$ts[2:N]-combined.M7.ETAS.cat$ts[1:N-1]

directory <-getwd()
directory
write.csv(iet, "New_Interevent_time_catalog.csv")
```

# Plot an image of the combined catalogue

```{r}
ggplot() + 
  geom_point(data = combined.M7.ETAS.cat, aes(x=ts, y=magnitudes), color='green') + 
  xlim(0, modelledDuration) +
  ggtitle("Background ETAS in time")

ggplot() + 
  geom_point(data = combined.M7.ETAS.cat, aes(x=ID, y=magnitudes), color='red') + ggtitle("Background ETAS in ID")

```

# Create a picture for results 

```{r}
N=length(combined.M7.ETAS.cat$ts)
iet =combined.M7.ETAS.cat$ts[2:N]-combined.M7.ETAS.cat$ts[1:N-1]

directory <-getwd()
directory
write.csv(iet, "New_Interevent_time_catalog.csv")
```

